NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-10 ms_nihao_budget.tex
thank referee
remove bold face enviroment

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes {\bf are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.}
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with {\bf recent} observational estimates.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
{\bf Several theoretical studies with cosmological simulations
have constrained the phase and cosmological environments of
the potential reservoirs of the missing baryons 
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.}

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons. \hi{} and metal absorption lines are
  expected  to signpost such diffuse baryonic content. \hi{} is mainly
  from gas with temperature T $\sim 10^4$ K so that it is able to
  detect cold gas in the CGM.  Meanwhile, theoretical work has
  predicted that a substantial  portion of the CGM is in the warm or
  hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
  through photoionization, accretion shocks or shocks caused by
  galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
  10^{4.5-7}$ K, so the detection is dominated by metal lines,
  e.g. \ovi{}.}  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
  Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  {\bf A number of large volume
  cosmological simulations \citep{Ford13, Ford15, Suresh15b,
    Oppenheimer16} and zoom-in cosmological simulations
  \citep{Stinson12, Hummels13, Shull14} have given predictions for the
  \hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
  column density profile of \ovi{} and \hi{} in the CGM of galaxies
  from the NIHAO \citep{Wang15} cosmological hydrodynamical
  simulation suite with observations, studied the covering fraction of
  dense \hi{}, looked at the shape of the CGM and its chemical
  composition. The conclusion shows the simulations can reproduce the
  observation properties well.}

  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project.
{\bf Reproducing the stellar mass content in dark matter haloes both
  today and in the past has been a formidable challenge for cosmological galaxy
  formation simulations \citep{Weinmann12, Hopkins14}. Even the latest
  state-of-the art simulations have trouble: the ILLUSTRIS simulation
  \citep{Vogelsberger14} strongly overpredicts the stellar masses in
  dwarf galaxy haloes $(M_{200} \lta 10^{11}\Msun)$, while the EAGLE
  simulations \citep{Schaye15} underpredict the peak of the star
  formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
  contrast, the} NIHAO galaxies are consistent with the stellar mass
vs halo mass relations from halo abundance matching since redshift
$z\sim 4$ \citep{Wang15}, the galaxy star formation rate vs stellar
mass relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore, the
simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

@@

The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
function of the halo mass is captured using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which is 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes.}

@@

{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
  gas in different phases at $z=0$, normalized to the total baryonic
  mass profile, such that, in the region far away from central galaxy
  where the stars are rare, for a given halo the four phases add up to
  unity.  All simulations share a common attribute.  The cold gas (T$<
  10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
  where most stars in galaxies form.  In contrast, the cool ($10^4$K
  $<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
  located at large distances with roughly constant fractions up to 2
  times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
  for all galaxies in the NIHAO sample, with the maximum hot gas
  fraction at any radius being  less than 5\%.}

{\bf Despite these similarities, we find a considerably higher proportion
  of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
  in the whole corona region.  For higher mass galaxies, warm-hot gas
  dominates the corona  which signals higher efficiency  of feedback.
  Even beyond the virial radius, the cool and warm-hot gas has similar
  features as the gas within virial radius which reveals the gas
  surrounding galaxies within large distance is the major reservoir of
  baryons.}

@@

{\bf To estimate how far the baryons escape, we measured the radius,
  $\Rbar$, within which the total baryon mass equals to the fiducial
  baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
  the true extent of the missing baryons since the baryon mass
  includes gas and stars that belong to nearby lower mass haloes.
  Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
  function of the virial mass.  We find the baryon radius generally
  increases with virial mass. But when normalized by the virial
  radius, the distance baryons are ejected to span a similar range of radii
  $\Rbar/R_{200}\sim 2-6$.}

@@

{\bf In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
  phase) inside the virial radius (blue points) and between  the
  virial and baryon radii (red points).
  %
  The fractions of cold gas,
  $f_{\rm cold}$, are shown in the upper-left panel.  Inside the
  virial radius $f_{\rm cold}$ increases gradually from zero at a halo
  mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
  $10^{12}\Msun$.  The gas outside the virial radius has the opposite
  and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
  $10^{10}\Msun$ and decreases to zero by halo masses of
  $10^{11}\Msun$.
  %
  The fractions of cool gas, $f_{\rm cool}$, are
  shown in the upper-right panel.  Inside the virial radius, $f_{\rm
    cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
  and declines to less than 10\% below and above halo masses of
  $10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
  is more cool gas outside than inside the virial radius.  In haloes
  of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
  less than 10\% by a halo mass of $10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
lower-left panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.}

@@

The observations and the simulations match well in every phase {\bf
  except} the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected {\bf cool gas too far}, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   {\bf However, \citet{Stern16} developed a new method to
  constrain the physical conditions in the cool CGM from measurements
  of ionic  columns densities. This new method combines the
  information available from different sightlines during the photoionization
  modeling, and was applied to the COS-HALOs data,  yielding a total
  cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
  which is shown by the green hashed bar in Fig~\ref{fig:budget} and
  is in good agreement with our prediction.  As the
  Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
  the most important component in CGM so that the more accurate
  knowledge of the physical properties of CGM are necessary to better
  understand the role of the CGM in galaxy formation.}
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\item {\bf Cold gas ($T<10^4$K) is mostly restricted to be within
      0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
      the corona at low masses ($M_{200}\lta 3\times 10^{11} \Msun$)
      while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
      masses ($M_{200}\gta 3\times 10^{11} \Msun$).}

@@

\item {\bf Cool gas is a major component of the total baryons within
      R$_{\rm bar}$, most of which is outside of the virial radius.}

@@

\item {\bf For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
      which is significantly lower than the observations from COS-HALOs
      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
      analysis of \citet{Stern16}.}

@@

{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
%
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations.
%
AAD, GSS and AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
%
LW acknowledges support of the MPG-CAS student programme.
%
XK acknowledge the support from 973 program (No. 2015CB857003,
2013CB834900), NSFC project No.11333008 and the ``Strategic Priority
Research Program the Emergence of Cosmological Structures'' of the
CAS(No.XD09010000).

>>>>

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with recent observational estimates.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Several theoretical studies with cosmological simulations
have constrained the phase and cosmological environments of
the potential reservoirs of the missing baryons 
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is a major potential  reservoir
of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to
detect cold gas in the CGM.  Meanwhile, theoretical work has
predicted that a substantial  portion of the CGM is in the warm or
hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
through photoionization, accretion shocks or shocks caused by
galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
10^{4.5-7}$ K, so the detection is dominated by metal lines,
e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  A number of large volume
cosmological simulations \citep{Ford13, Ford15, Suresh15b,
  Oppenheimer16} and zoom-in cosmological simulations
\citep{Stinson12, Hummels13, Shull14} have given predictions for the
\hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
column density profile of \ovi{} and \hi{} in the CGM of galaxies
from the NIHAO \citep{Wang15} cosmological hydrodynamical
simulation suite with observations, studied the covering fraction of
dense \hi{}, looked at the shape of the CGM and its chemical
composition. The conclusion shows the simulations can reproduce the
observation properties well.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project.
Reproducing the stellar mass content in dark matter haloes both
today and in the past has been a formidable challenge for cosmological galaxy
formation simulations \citep{Weinmann12, Hopkins14}. Even the latest
state-of-the art simulations have trouble: the ILLUSTRIS simulation
\citep{Vogelsberger14} strongly overpredicts the stellar masses in
dwarf galaxy haloes $(M_{200} \lta 10^{11}\Msun)$, while the EAGLE
simulations \citep{Schaye15} underpredict the peak of the star
formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
contrast, the NIHAO galaxies are consistent with the stellar mass
vs halo mass relations from halo abundance matching since redshift
$z\sim 4$ \citep{Wang15}, the galaxy star formation rate vs stellar
mass relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore, the
simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=budget_res.eps,width=0.48\textwidth}
}
\caption{Linear fractional baryon content of our NIHAO simulations  as a
  function of halo mass. }
\label{fig:budget_res}
\end{figure}

@@

The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
function of the halo mass is captured using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
which is 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes.

@@

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from central galaxy
where the stars are rare, for a given halo the four phases add up to
unity.  All simulations share a common attribute.  The cold gas (T$<
10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K
$<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
in the whole corona region.  For higher mass galaxies, warm-hot gas
dominates the corona  which signals higher efficiency  of feedback.
Even beyond the virial radius, the cool and warm-hot gas has similar
features as the gas within virial radius which reveals the gas
surrounding galaxies within large distance is the major reservoir of
baryons.

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals to the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass
includes gas and stars that belong to nearby lower mass haloes.
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass.  We find the baryon radius generally
increases with virial mass. But when normalized by the virial
radius, the distance baryons are ejected to span a similar range of radii
$\Rbar/R_{200}\sim 2-6$.

@@

In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
phase) inside the virial radius (blue points) and between  the
virial and baryon radii (red points).
%
The fractions of cold gas,
$f_{\rm cold}$, are shown in the upper-left panel.  Inside the
virial radius $f_{\rm cold}$ increases gradually from zero at a halo
mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
$10^{12}\Msun$.  The gas outside the virial radius has the opposite
and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
$10^{10}\Msun$ and decreases to zero by halo masses of
$10^{11}\Msun$.
%
The fractions of cool gas, $f_{\rm cool}$, are
shown in the upper-right panel.  Inside the virial radius, $f_{\rm
  cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
and declines to less than 10\% below and above halo masses of
$10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
is more cool gas outside than inside the virial radius.  In haloes
of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
less than 10\% by a halo mass of $10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
lower-left panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.

@@

The observations and the simulations match well in every phase except
 the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected cool gas too far, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   However, \citet{Stern16} developed a new method to
constrain the physical conditions in the cool CGM from measurements
of ionic  columns densities. This new method combines the
information available from different sightlines during the photoionization
modeling, and was applied to the COS-HALOs data,  yielding a total
cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
which is shown by the green hashed bar in Fig~\ref{fig:budget} and
is in good agreement with our prediction.  As the
Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
the most important component in CGM so that the more accurate
knowledge of the physical properties of CGM are necessary to better
understand the role of the CGM in galaxy formation.
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\item Cold gas ($T<10^4$K) is mostly restricted to be within
      0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
      the corona at low masses ($M_{200}\lta 3\times 10^{11} \Msun$)
      while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
      masses ($M_{200}\gta 3\times 10^{11} \Msun$).

@@

\item Cool gas is a major component of the total baryons within
      R$_{\rm bar}$, most of which is outside of the virial radius.

@@

\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
      which is significantly lower than the observations from COS-HALOs
      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
      analysis of \citet{Stern16}.

@@

We thank the anonymous referee whose suggestions greatly 
improve the paper.
{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
%
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations.
%
AAD, GSS and AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
%
LW acknowledges support of the MPG-CAS student programme.
%
XK acknowledge the support from 973 program (No. 2015CB857003,
2013CB834900), NSFC project No.11333008 and the ``Strategic Priority
Research Program the Emergence of Cosmological Structures'' of the
CAS(No.XD09010000).
